---
title: "Danish casualties in the German army 1914-1921"
author: "Tjebbe A. Veltman"
date: "2023-01-08"
output: html_document
---
#Turning on library
```{r}
library(tidyverse)
```
```{r}
library(markdown)
```

```{r}
knitr::opts_chunk$set(echo = TRUE,
                      message=FALSE)
```
#appointing the data
```{r}
Data <- read.csv(file = 'data/soldiers_2.csv')
```
#test
```{r}
head(Data)[12]
```
#appointing data
```{r}
names(Data)[19] = "Country_of_death"
```
```{r}
names(Data)[18] = "Place_of_death"
```
```{r}
names(Data)[12] = "Age_of_death"
```
```{r}
names(Data)[20] = "Date_of_death"
```
```{r}

```
#apponting data again
```{r}
Country_of_death <- Data[19]
```
```{r}
Place_of_death <- Data[18]
```
```{r}
Age_of_death <- Data[12]
```
```{r}
Date_of_death <- Data[20]
```
#making the first graph
```{r}
Data_Countries_of_death <- Data %>% 
  count(Country_of_death, sort = TRUE) %>% 
  head(15)

ggplot(Data_Countries_of_death, aes(y = reorder(Country_of_death, n), x = n)) + 
  geom_bar(stat = "identity") +
  theme_light() +
  labs(title = "Death by country", x = "deaths", y = "country")
```




#second graph
```{r}
Data_Place_of_death <- Data %>% 
  count(Place_of_death, sort = TRUE) %>% 
  head(15)

ggplot(Data_Place_of_death, aes(y = reorder(Place_of_death, n), x = n)) + 
  geom_bar(stat = "identity") +
  theme_light() +
  labs(title = "Death by place", x = "deaths", y = "area")
```

#third graph
```{r}
Data_Age_of_death <- Data %>% 
  count(Age_of_death, sort = TRUE) %>% 
  head(15)

ggplot(Data_Age_of_death, aes(y = reorder(Age_of_death, n), x = n)) + 
  geom_bar(stat = "identity") +
  theme_light() +
  labs(title = "Death by Age", x = "deaths", y = "age group")
```
#fourth graph
```{r}
Data_Date_of_death <- Data %>% 
  count(Date_of_death, sort = TRUE) %>% 
  head(15)

ggplot(Data_Date_of_death, aes(y = reorder(Date_of_death, n), x = n)) + 
  geom_bar(stat = "identity") +
  theme_light() +
  labs(title = "Death by date", x = "deaths", y = "date")
```

#finishing comments; i want to thank Adela Sobotkova for teaching digital methods. Athough i wasn't the best at this course, i enjoyed her teachings and the class enviorment. Hopefully in the future i can  practise more with it, and become better at Rstudio. OpenRefine is a tool i took a liking to, and for sure will use in the future




